# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r cache=TRUE}
rawData <- read.csv(unz("activity.zip",  filename = "activity.csv"))
summary(rawData)
```


## What is mean total number of steps taken per day?
```{r cache=TRUE}
mean.withNA <- function(x){mean(x, na.rm = TRUE)}
stepsByDay <- aggregate(steps ~ date, rawData, mean.withNA)
meanSteps <- mean(stepsByDay[,2])
medianSteps <- median(stepsByDay[,2])
hist(stepsByDay[,2], main = "Distribution of quantity of steps taken each day", xlab = "Steps per day")
```

The mean of steps taken per day is `r meanSteps` and the median is `r medianSteps`.


## What is the average daily activity pattern?

```{r cache=TRUE}
stepsByInterval <- aggregate(steps ~ interval, rawData, mean.withNA)
maxInterval <- stepsByInterval[which.max(stepsByInterval[,2]),1]
plot(stepsByInterval[,1], stepsByInterval[,2], xlab="Average steps quantity", ylab="Interval", type="l")
```

The max is reached at the interval `r maxInterval`.

## Imputing missing values
```{r cache=TRUE}
naQuantity <- sum(is.na(rawData[,1]))

stepsByInterval.filled <- aggregate(steps ~ interval, rawData, mean.withNA)

rawData.filled <- rawData

rawData.filled[is.na(rawData.filled[, "steps"]), "steps"] <-
  
  stepsByInterval.filled[which(stepsByInterval.filled$interval == rawData.filled[is.na(rawData.filled[, "steps"]), "interval"]), "steps"]

rm(stepsByInterval.filled)
#rawData.filled[is.na(rawData[,1]),1] <- 0

stepsByDay.filled <- aggregate(steps ~ date, rawData.filled, mean)
meanSteps.filled <- mean(stepsByDay.filled[,2])
medianSteps.filled <- median(stepsByDay.filled[,2])
hist(stepsByDay[,2], main = "Distribution of quantity of steps taken each day", xlab = "Steps per day")
```

The data set has `r naQuantity` missing values.

The strategy used to fill the missing values is just replace it by zeros.

The mean of steps taken per days is `r meanSteps.filled` and the median is `r medianSteps.filled`.

Indeed, as we can expect the mean does not differ from the original data, but the median suffer a slight change.


## Are there differences in activity patterns between weekdays and weekends?
```{r cache=TRUE}
library(lattice)
weekDays<- sapply(rawData.filled$date, function(x){ ifelse(as.POSIXlt(as.Date(x))$wday < 6, "Weekday", "Weekend")})
stepsByIntervalByWeekdays <- aggregate(steps~ interval * weekDays, rawData.filled,mean)
xyplot(steps~interval | weekDays, data = stepsByIntervalByWeekdays, type="l")
```

